Adaptive Scheduling of Scientific Workflows\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-05-07 main.tex
first picture about the normal cluster

    On the normal cluster and among small workflows, the makespans produced by \heftbl and \heftblc are $1$\% worse than the baseline,
    \heftmm $19$\% worse.
    For middle-sized ones \heftmm is $12.3$\% worse, the rest is also $1-2$\% worse.
    For the big workflows however, the results of \heftbl and \heftblc are $<1$\% worse and \heftmm is only $9$\% worse.
    The heuristics pay off more on larger workflows.
    \subsubsection{Memory usage}
    Minimizing memory usage is an interesting measure of the quality of the solution produced by a heuristic.
    We studied the average peak memory consumption in our cluster.
    We looked at the maximum memory usage on each processor during a task execution, and averaged it over all processors
    in the execution environment.

>>>>

    The excess makespans produced by the heuristics are shown in Figure~\ref{fig:excess-ms}.
    On the normal cluster and among small workflows, the makespans produced by \heftbl and \heftblc are virtually indistinguishable
    from those of the baseline (no change and $0.4$\% change), while \heftmm produces  $18$\% worse makespans.
    For middle-sized ones \heftmm is $9$\% worse,  \heftblc $0.9$\% worse.
    For the big workflows however, while results of \heftbl and \heftblc are still barely worse ($<1$\% worse),
     \heftmm is only $5.8$\% worse.
    The heuristics pay off more on larger workflows.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.495\columnwidth] {images/ms-relative-3groups}
        \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm for different . Smaller is better.}
       \label{fig:excess-ms}
        \vspace{-0.3cm}
    \end{figure}
    \subsubsection{Memory usage}
    Minimizing memory usage is an interesting measure of the quality of the solution produced by a heuristic.
    We studied the average peak memory consumption in our cluster.
    We looked at the maximum memory usage on each processor during a task execution, and averaged it over all processors
    in the execution environment.
